Mapping mutational effects along the evolutionary landscape of HIV envelope

### 2018-02-26 paper/manuscript.tex
Add response to minor comment 4

@@

The color spectrum is similar to the one in (A) and (B), but is colored from blue to \textit{grey} to red for increased visibility of the grey residues in the hydrophobic network.

>>>>

We used a color scale that only ranges between significance values of $-6 < \log_{10}Q < 6$, which decreases the resolution between a small number of sites with extreme values, but provides greater resolution among other sites.
Sites for which we lack $\omega_r$ estimates are colored black.

@@
